A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator

### 2016-05-19 paper3_manuscript.tex
20160519

Besides the issue on repressing the chattering, the fast convergence of the SMC scheme is also a hot subject. Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and some accelerating operations usually occur in this two phases. The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques can just guarantee the asymptotically convergence. For achieving a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase to complete the global finite time convergence. Owing to the global finite time convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal. Feng et al. presented a global terminal sliding mode algorithm for manipulating the rigid robot, and produced the control design by using Lagrangian dynamic expression~\cite{feng2002non}. In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of terminal and super-twisting sliding-mode, providing a convergence control in finite time. \par
According to the achievements mentioned above, one can find that the conventional terminal sliding mode manifold design techniques are similar, since they are all based on the single variable finite time control, in another words, the sliding mode dynamics only involves the individual variable and its derivative essentially~\cite{mu2016switching}. This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergent time in some extent. In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the two-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time can be obtained easily. Also, the nonsingularity and chattering suppression are available in the scheme. \par

@@

As described in~\cite{moulay2006finite}, it is assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:

@@

where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ can converge to the origin for any given $t_0$, and typically the finite convergent time $t_r$ can be given as follows:

@@

For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs can be given according the following theorem.

@@

Hence, the system (\ref{eq:two order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.\par

@@

The total convergent time can be calculated by dividing the convergence into two phase with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ can be given out directly:

@@

On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible. Consider the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:

@@

where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergent time can be described as:

@@

After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically. Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed. Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$. Admittedly, the variety of $\lambda$ is only modestly helpful in this approaching time regulation due to its limited effect on $V(t_0)$. $\eta$ is said to be an ''approaching speed'' according to its function, a suitable selection of which will adjust the approaching time as desired in some extent. Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it can be defined as the management parameter of the sliding status.

@@

For the proposed designs, the parameter $\gamma$ can be defined as different scalar for the individual input, if so, one can produce the total convergent time as:

@@

Considering the two-order system (\ref{eq:two order system}), the terminal sliding mode manifold can be designed as:

@@

and $u_s>0$ can be determined according to the requirements of the performance.\par

@@

Select $\bm q_d$ as the desired state of the Lagrangian system~(\ref{eq:lagrangian system}), and the derivative of $\bm q_d$ is designated as $\dot {\bm q}_d$. Hence the state error can be given out intuitively:

@@

furthermore, one can obtain the corresponding input as follows to stabilize the system~(\ref{eq:lagrangian system}) as desired in finite time.

@@

in which $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it is assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.

@@

the derivative of which can be described as

@@

and $\Vert\bm s\Vert\neq 0$, hence, the Lyapunov stability has been proved, meaning that the system will reach the desired manifold~(\ref{eq:lagrangian manifold}) in finite time. Once the reaching condition is satisfied, one can achieve a reduced system by substituting $\bm s = 0$ into the system~(\ref{eq:lagrangian system}). It owns the form, similar to Eq.~(\ref{eq:normal sliding manifold}), and therefore, one can adopt Theorem \ref{theorem:2} to drive the reduced system converging to the origin in finite time. The proof is completed.

@@

At this point, the DTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator. Consider a $n$-link robotic manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as

@@

Referring to Theorem \ref{theorem:4}, one can obtain the DTSM input for the even $n$-link manipulator. Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DTSM scheme.

@@

The singularity of the DTSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.

@@

One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically. For handling the chattering, the $sign(x)$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.

@@

and one can produce a MDTSM control scheme conveniently. It is obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:

@@

and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold. Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation two order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$. In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actual value obviously. In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance. Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
This section will give a set of simulation to examine the performance of the MDTSM control in tracking the certain angle condition. The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$. In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 100$. The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
\begin{align}
\begin{split}
\bm s &= \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)\rfloor\\
\bm\tau &= \bm u_0+\bm u_1 +\bm u_2\\
\bm u_0 &= -M_0(\bm q)C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}\rfloor\\
\bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.
\end{split}
\end{align}
where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.\par
The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}. Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates. One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control. More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDTSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison. Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{Response of $q_1$ channel}
\label{Figure:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
\caption{Response of $q_2$ channel}
\label{Figure:5}
\end{figure}
The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section. Particularly, one can continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
\begin{align*}
&(\bm q_0^T, \dot{\bm q}_0^T)= (1.5,1.5,0,0)\\
&{\bm q}_d^T=(1.25-(1/5)e^{-t}+(1/20)e^{-4t},1.25+(9/40)e^{-t}-(1/4)e^{-2t})
\end{align*}\par
The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDTSM scheme. The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
\caption{Tracking performance of $q_1$ channel}
\label{Figure:6}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
\caption{Tracking performance of $q_2$ channel}
\label{Figure:7}
\end{figure}
\section{Conclusion}\label{sec:5}
A DTSM control for n-link robotic manipulator has been presented. The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design. The control scheme can guarantee the reaching condition of the desired sliding manifold, meanwhile the system states can converge to the origin along the desired manifold. Also, the entire convergent time can be calculated accordingly. Developing the basic DTSM yields the MDTSM control, providing a solution to eliminating chattering, avoiding singularity and fast convergence. For dealing with the under actuated characteristics which may appear in the system, the hierachical sliding mode technique will be considered to introduce into the control scheme, however, the control parameters selection is still a challenge.
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}

>>>>

Besides the issue on repressing the chattering, the fast convergence of the SMC scheme is also a hot subject. Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and some accelerating operations usually occur in this two phases. The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques are able to guarantee the asymptotically convergence. For achieving a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase to complete the global finite time convergence. Owing to the global finite time convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal. Feng et al. presented a global terminal sliding mode algorithm for manipulating the rigid robot, and produced the control design by using Lagrangian dynamic expression~\cite{feng2002non}. In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of terminal and super-twisting sliding-mode, providing a convergence control in finite time. \par
According to the achievements mentioned above, one can find that the conventional terminal sliding mode manifold design techniques are similar, since they are all based on the single variable finite time control, in another words, the sliding mode dynamics only involves the individual variable and its derivative essentially~\cite{mu2016switching}. This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergent time in some extent. In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the two-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time is obtained easily. Also, the nonsingularity and chattering suppression are available in the scheme. \par

@@

As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:

@@

where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V(t)$ converges to the origin for any given $t_0$, and typically the finite convergent time $t_r$ can be given as follows:

@@

For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs are addressed according the following theorem.

@@

Hence, the system (\ref{eq:two order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time is calculated according to the finite time convergence theory.\par

@@

The total convergent time can be calculated by dividing the convergence into two phase with respect to the relation between the system and the manifold, namely, the approaching phase and the sliding phase, and specifically, according to Lemma \ref{lemma:2}, the total finite convergent time $t_f$ is calculated from:

@@

On the basis of Theorem \ref{theorem:1}, we proceed to develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible. Consider the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which are described by following expressions:

@@

where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value. The total finite convergent time is calculated from:

@@

After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically. Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed. Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$. Admittedly, the variety of $\lambda$ is only modestly helpful in this approaching time regulation due to its limited effect on $V(t_0)$. $\eta$ is said to be an ''approaching speed'' according to its function, a suitable selection of which will adjust the approaching time as desired in some extent. Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it's able to be defined as the management parameter of the sliding status.

@@

For the proposed designs, the parameter $\gamma$ may be defined as different scalar for the individual input, if so, one can produce the total convergent time as:

@@

Considering the two-order system (\ref{eq:two order system}), the terminal sliding mode manifold is designed as:

@@

and $u_s>0$ is determined according to the requirements of the performance.\par

@@

Select $\bm q_d$ as the desired state of the Lagrangian system~(\ref{eq:lagrangian system}), and the derivative of $\bm q_d$ is designated as $\dot {\bm q}_d$. Hence the state error is stated as:

@@

furthermore, the corresponding input follows to stabilize the system~(\ref{eq:lagrangian system}) as desired in finite time.

@@

in which $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it's assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.

@@

the derivative of which is described as

@@

and $\Vert\bm s\Vert\neq 0$, hence, the Lyapunov stability has been proved, meaning that the system will reach the desired manifold~(\ref{eq:lagrangian manifold}) in finite time. Once the reaching condition is satisfied, one can achieve a reduced system by substituting $\bm s = 0$ into the system~(\ref{eq:lagrangian system}). It owns the form, similar to Eq.~(\ref{eq:normal sliding manifold}), and therefore, adopting Theorem \ref{theorem:2} drives the reduced system converging to the origin in finite time. The proof is completed.

@@

At this point, the DTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator. Consider a $n$-link robotic manipulator in which $n$ is an even number, and the desired sliding manifold follows 

@@

Referring to Theorem \ref{theorem:4}, it's easy to obtain the DTSM input for the even $n$-link manipulator. Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension is able to be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DTSM scheme.

@@

The singularity of the DTSM scheme for the robotic manipulator can be removed by using the technique introduced in Theorem \ref{theorem:3}.

@@

One can also use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically. For handling the chattering, the $sign(x)$ is replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.

@@

and a MDTSM control scheme is produced conveniently. It's obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:

@@

and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ are determined accordingly to guarantee the reaching condition of the desired sliding manifold. Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation two order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$. In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actual value obviously. In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance. Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
This section will give a set of simulation to examine the performance of the MDTSM control in tracking the certain angle condition. The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$. In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 100$. The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
\begin{align}
\begin{split}
\bm s &= \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)\rfloor\\
\bm\tau &= \bm u_0+\bm u_1 +\bm u_2\\
\bm u_0 &= -M_0(\bm q)C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}\rfloor\\
\bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.
\end{split}
\end{align}
where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.\par
The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}. Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates. Concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control. More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDTSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison. Therefore these results show that the MDTSM control scheme is able to achieve the regulation of the manipulator effectively.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{Response of $q_1$ channel}
\label{Figure:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
\caption{Response of $q_2$ channel}
\label{Figure:5}
\end{figure}
The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section. Particularly, we continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
\begin{align*}
&(\bm q_0^T, \dot{\bm q}_0^T)= (1.5,1.5,0,0)\\
&{\bm q}_d^T=(1.25-(1/5)e^{-t}+(1/20)e^{-4t},1.25+(9/40)e^{-t}-(1/4)e^{-2t})
\end{align*}\par
The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDTSM scheme. The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
\caption{Tracking performance of $q_1$ channel}
\label{Figure:6}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
\caption{Tracking performance of $q_2$ channel}
\label{Figure:7}
\end{figure}
\section{Conclusion}\label{sec:5}
A DTSM control for n-link robotic manipulator has been presented. The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design. The control scheme is able to guarantee the reaching condition of the desired sliding manifold, meanwhile the system states converge to the origin along the desired manifold. Also, the entire convergent time can be calculated accordingly. Developing the basic DTSM yields the MDTSM control, providing a solution to eliminating chattering, avoiding singularity and fast convergence. For dealing with the under actuated characteristics which may appear in the system, the hierachical sliding mode technique will be considered to introduce into the control scheme, however, the control parameters selection is still a challenge.
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}
